### 2018-12-17 Sections/intro_to_QM.tex
Added into to QM to main text

\documentclass[aps,pra,twocolumn,amsmath,amssymb,nofootinbib,superscriptaddress]{revtex4}

\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}
\usepackage{braket}
\usepackage{lettrine}

\newcommand{\dropcap}[2]{\lettrine[lines=2, findent=3pt, nindent=0pt]{#1}{#2}}

\begin{document}

%
% Introduction to Quantum Mechanics
%

\part{Introduction to quantum mechanics}

@@

\end{document}

>>>>

\dropcap{T}{o} make the upcoming discussion accessible to those from a non-quantum background, we will briefly level the playing-field by presenting an overview of the mathematical formulation of quantum mechanics, all of which fits within the confines of familiar linear algebra.

The laws of quantum mechanics are inherently different to those of classical mechanics, and bring with them their own unique notation for:
\begin{itemize}
	\item The representation of quantum states.
	\item The evolution of quantum systems.
	\item Measurement of quantum states.
\end{itemize}
We review all of these formalisms in the upcoming sections.

The key conceptual differences between classical and quantum mechanics are:
\begin{itemize}
	\item Superposition: the ability of quantum systems to be in multiple states simultaneously.
	\item Complex amplitudes: quantum states are not governed by classical probabilities, but by \textit{quantum amplitudes}, which are complex numbers.
	\item Entanglement: a type of non-local quantum correlation, stronger than any possible classical correlation.
	\item Unitary evolution: the evolution of quantum systems is restricted to being described by unitary operators.
	\item Measurement collapse: the measurement of a quantum system changes its state in general.	
\end{itemize}
All of these phenomena will become clear as we present the relevant mathematical constructions.

@@

\comment{Index}
